---
output:
  html_document: default
  pdf_document: default
---
## The Spark Foundation "GRIP JUNE 2021"
## Task 1:- Prediction Using Supervised ML
### By:- Aakriti Pankaj




**Objective:- To predict percentage of a student if he/she study for 9.25 hrs/day.**

**Solution:-**

Read the data from url. Here is the code Chunk for reading url:-
```{r}
data <- read.csv(url("https://raw.githubusercontent.com/AdiPersonalWorks/Random/master/student_scores%20-%20student_scores.csv"))
data
```
Plot the relationship between Hours and Scores. Here is the code chunk:-
```{r}
plot(data$Hours, data$Scores, col = "blue", pch = 3, xlab = "Hours", ylab = "Scores")
title(main = "Graph 1:- Relationship between Hours and Scores")
```

From graph 1, we can see that there is positive relationship between Hours and Scores.

Partiton the data into training set and test set. Here is the code chunk:-
```{r}
library(lattice)
library(ggplot2)
library(caret)
set.seed(22)
inTrain <- createDataPartition(y = data$Scores, p = 0.6, list = FALSE)
traindata <- data[inTrain,]
testdata <- data[-inTrain,]
traindata
```
Fit a linear model. Here is the code chunk:-
```{r}
lm1 <- lm(Scores ~ Hours, data = traindata)
summary(lm1)
```
Plot prediction of training set and test set with best line of fit. Here is the code chunk:-
```{r}
plot(traindata$Hours, traindata$Scores, pch = 3, col = "blue", xlab = "Hours", ylab = "Scores")
lines(traindata$Hours, predict(lm1), lwd = 3)
title(main = "Graph 2:- Relationship between Hours and Scores of training set")
plot(testdata$Hours, testdata$Scores, pch = 3, col = "blue", xlab = "Hours", ylab = "Scores")
lines(testdata$Hours, predict(lm1, newdata = testdata), lwd = 3)
title(main = "Graph 3:- Relationship between Hours and Scores of Test set")
```

From graph 2 and 3, we can see that there is linear relationship between Hours and Scores of both training and test data set.

Calculate training set error. Here is the code chunk:-
```{r}
sqrt(sum((lm1$fitted - traindata$Scores)^2))
```
Calculate test set error. Here is the code chunk:-
```{r}
sqrt(sum((predict(lm1, newdata = testdata) - testdata$Scores)^2))
```
Predict score if a student study for 9.25 hrs/ day. Here is the code chunk:-
```{r}
newdata <- data.frame(Hours = 9.25)
predict(lm1, newdata)
```
As a result, we get 96.18837% score.

**Conclusion:-**
Using Supervised ML model, predicted percentage of a student is 96.18837% if he/she study for 9.25 hrs/day.